---
name: Francis
surname: Rosales
position: "Service Greeter"
phone: +1 (909) 781-4753
www: yourwebsite.com
email: "frrosales@cpp.com"
github: https://github.com/fraros210
linkedin: https://www.linkedin.com/in/francis-rosales-704a91383/
date: "`r format(Sys.time(), '%B %Y')`"
output: 
  vitae::latexcv:
    theme: classic
header-includes:
   - \usepackage{enumitem}
   - \setlist[itemize]{nosep, left=0pt}
   - \setlist[enumerate]{nosep, left=0pt}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

if (!requireNamespace(c("tinytex","vitae","tibble"), quietly = TRUE)) {
  install.packages(c("tinytex","vitae","tibble"))
}

if (Sys.which("pdflatex") == "" && !tinytex::is_tinytex()) {                    
  message("► TinyTeX not found – installing")
  tinytex::install_tinytex()        
} else {
  message("✓ LaTeX present – no installation needed.")
}

library(vitae)
library(tibble)
```

# Professional Summary

Currently, I hold  a position working at the Claremont Toyota Dealership in Claremont, California as a Service Greeter. I retain skills in customer service and sanitation, maintaining the work facility, and running errands when needed to (bringing paperwork, refilling the printers with paper, carrying heavy objects, etc). I’ve recently acquired service writing skills as a hybrid express writer, meaning that I am mobilized as one when there is a high volume of customers on the service drive. My main objective is to utilize the additional skills that I have acquired from obtaining my automotive certificate and business degree into becoming a service advisor and to further carry out excellent customer service and professionalism within the service department.


# Technical Skills

-tribble(
  ~ Degree, ~ Year, ~ College, ~ Institution,
  "Bachleor of [Business Management]", "2025 – Expected Graduation 2026", "[College of Business]", "[California State Polytechnic University, Pomona]",
  "General Automotive Service Certificate of Achievement", "2020 – 2024", "[Automotive Technology]", "[Rio Hondo Community College]",
  "Business Administration for Transfer", "2020 – 2024", "[Department of Business]", "[Rio Hondo Community College]"
) %>%
  detailed_entries(Degree, Year, College, Institution)ren

```{r}
tribble(
  ~ Years, ~ Company, ~ Duties, ~ Title,

  "August 2024 – Present", "Claremont Toyota",
  list(
    "Summarize responsibility or achievement \\#1.",
    "Highlight tools, technologies, or methods used.",
    "Mention metrics, goals, or impact if possible.",
    "Add communication or leadership responsibilities here."
  ),
  "Job Title",

  "Month YYYY – Month YYYY", "Another Company or Team",
  list(
    "Led a project or team focused on [insert focus].",
    "Collaborated cross-functionally with [departments/roles].",
    "Managed content, campaigns, or dashboards.",
    "Contributed to strategic planning or reporting."
  ),
  "Job Title"

) %>%
  detailed_entries(
    what = Title,
    when = Years,
    with = Company,
    why = Duties
  )
```